KIN: A method to infer relatedness from low-coverage ancient DNA

### 2022-04-07 paper_overleaf/main.tex

\paragraph{Critical Values}
 To investigate the limits of our method, we plotted the true-positive and false-positive rates when we use a particular difference in log-likelihood as a cutoff( Fig.\ref{figS10:cutoff},  Fig.\ref{fig3:Comparison_READ_KIN}).   Fig.\ref{figS10:cutoff} shows that for all relatedness cases except for $3^{rd}$-degree, the false positive rate is below $5\%$ even when simply selecting the model with the highest likelihood. We observe that for $3^{rd}$-degree relatives, using a cutoff of 1.0 brings down the false positive rate close to $5\%$ for all coverages except 0.05x. Thus, we  recommended to use a cutoff of 1 for all cases where ROH or contamination are not a concern.

>>>>

\paragraph{Critical Values}
 To investigate the limits of our method, we plotted the true-positive and false-positive rates when we use a particular difference in log-likelihood as a cutoff( fig. S \ref{figS10:cutoff}). The figure shows that for all relatedness cases except for $3^{rd}$-degree, the false positive rate is below $5\%$ even when simply selecting the model with the highest likelihood. We observe that for $3^{rd}$-degree relatives, using a cutoff of 1.0 brings down the false positive rate close to $5\%$ for all coverages except 0.05x. Thus, we  recommended to use a cutoff of 1 for all cases where ROH or contamination are not a concern.
